Embodied Neuromorphic Benchmarks

### 2015-08-13 paper/paper.tex
Added calibration discussion

    Evaluating the effectiveness and performance of neuromorphic hardware is
    difficult.  It is even more difficult when the task of interest is an
    embodied task; that is, a task where the output from the neuromorphic
    hardware affects its future input through some environment.  However, embodied situations
    are one of the primary potential uses of neuromorphic hardware.  To address
    this, we present a methodology for embodied benchmarking that makes use
    of a hybrid of real physical embodiment and a type of ``minimal'' simulation.
    Minimal simulation has been shown to lead to robust real-world performance,
    while still maintaining the practical advantages of simulation, such as
    making it easy for the same benchmark to be used by many researchers.
    These benchmarks are flexible, in that they allow researchers to explicitly
    modify the benchmark to identify particular task domains where particular
    hardware excels.  To demonstrate the method, we present a novel benchmark
    where the task is to perform motor control on an arbitrary unknown system.

@@

To interface to the physical hardware, we installed the \texttt{ev3dev} operating
system (\texttt{http://ev3dev.org}), a Debian-based Linux system specifically developed
for the EV3.  We then installed and ran the \texttt{ev3\_link} program from \texttt{ev3dev-c}
(\texttt{https://github.com/in4lio/ev3dev-c}).  This allows the EV3 to listen for
UDP commands that tell it to set motor values and read sensor values.
Communication with a PC was over a USB link (although the system also
supports WiFi communication).  With constant communication, the system is
able to adjust the power sent to the motors $u$ and give position feedback
$q$ from those motors at a rate of around 300Hz.

Figure [???] shows the system being controlled by a simple PD controller.
The desired joint angle $q_d$ is varied randomly over time.  Notice that the
system consistently undershoots and overshoots the desired angle, due to
its inability to compensate for gravity.

In Figure [???], we show the result of using the adaptive controller algorithm.
The system quickly improves on the standard PD controller, learning to adjust
its control signal $u$ to compensate for the unknown external forces.

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=10cm]{logo1}% This is a *.jpg file
\end{center}
 \textbf{\refstepcounter{figure}\label{fig:01} Figure \arabic{figure}.}{ Enter the caption for your figure here.  Repeat as  necessary for each of your figures }
\end{figure}

>>>>

    Evaluating the effectiveness and performance of neuromorphic hardware is
    difficult.  It is even more difficult when the task of interest is an
    embodied task; that is, a task where the output from the neuromorphic
    hardware affects its future input through some environment.  However, embodied situations
    are one of the primary potential uses of neuromorphic hardware.  To address
    this, we present a methodology for embodied benchmarking that makes use
    of a hybrid of real physical embodiment and a type of ``minimal'' simulation.
    Minimal simulation has been shown to lead to robust real-world performance,
    while still maintaining the practical advantages of simulation, such as
    making it easy for the same benchmark to be used by many researchers.
    These benchmarks are flexible, in that they allow researchers to explicitly
    modify the benchmark to identify particular task domains where particular
    hardware excels.  To demonstrate the method, we present a novel benchmark
    where the task is to perform motor control on an arbitrary system with
    unknown external forces.

@@

To interface to the physical hardware, we installed the \texttt{ev3dev} operating
system (\texttt{http://ev3dev.org}), a Debian-based Linux system specifically developed
for the EV3.  We then installed and ran the \texttt{ev3\_link} program from \texttt{ev3dev-c}
(\texttt{https://github.com/in4lio/ev3dev-c}).  This allows the EV3 to listen for
UDP commands that tell it to set motor values and read sensor values.
Communication with a PC was over a USB link (although the system also
supports WiFi communication).  With constant communication, the system is
able to adjust the power sent to the motors $u$ and give position feedback
$q$ from those motors at a rate of around 200Hz.

Figure \ref{fig:ev3} shows the effects of adaptive control on this physical
system.  Without adaptation (i.e. with a simple PD controller), there system
state $q$ (the joint angle) overshoots the desired $q_d$.  This overshoot
is largest when $q$ is large.  This is because the external force applied to
the joint due to gravity is proportional to $sin(q)$.  The $q$ value also
overshoots and comes back part-way, due to physical momentum.

However, with adaptation (the right-hand side of Figure \ref{fig:ev3}),
the system learns to counteract this extra force due to gravity.  After
the first 5 seconds, the system is able to bring $q$ much closer to the
desired $q_d$.

Now that we have this physical example of the task out minimal simulation
benchmark is meant to cover, we can use it to calibrate the parameters of
the simulation.  For example, communication with the EV3 happens around
200Hz, meaning that there must be a delay on the order of 0.005 seconds.  Given
this, we set the delays in the simulation to be uniformly chosen between
0 and 0.01.  Importantly, we do not need to exactly measure the delay in the
EV3 robot --- we just make sure that the minimal simulation is worse.

For sensor noise, we note that the EV3 rotation encoders for the motors (the
devices that measure $q$) have a resolution of 0.0175 (1 degree).  This is a
very different sort of noise than the gaussian noise used in the simulation,
so we set the simulation noise to be much larger (uniformly distributed
between 0 and 0.1).  Similarly, the motor resolution is 0.01, as it accepts 
integer values up to 100, so we set the motor noise to be uniform between
0 and 0.1.

Finally, we can use the physical system to calibrate the relationship between
$T$ (the maximum torque applied by the motor) and $K_f$ (the scaling factor
of the external force).  After all, we do not want external forces that are
so strong that the system does not have enough strength to counteract them.
On the physical robot, in the worst-case scenario ($q=\pi/2$ or $-\pi/2$),
the motors must be driven at around 0.3 times their maximum strength to
balance the force of gravity.  (This can, of course, be adjusted by changing
the weight and its position on the end of the arm).  If we arbitrarily fix $K_f$ to 1 and randomly
generate external forces given the process described above, then 95\% of
the time we get values between -3.75 and +3.75.  Since we want the motors to
be strong enough to compensate for forces in that range, we set $T$ to 10.

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=18cm]{figures/fig_ev3}
\end{center}
 \textbf{\refstepcounter{figure}\label{fig:ev3} Figure \arabic{figure}.}{ Adaptive control of the EV3 lego robot used for calibrating the minimal simulation.
 The effects of adaptation over two different desired trajectories are shown.  Without adaptation, the joints $q$ do not reach the desired $q_d$ when $q_d$ is large (which
 is when the external force is largest).  With adaptation, $q$ is closer to $q_d$ after about 5 seconds, showing that the system has quickly learned to compensate.}
\end{figure}
